A Survey on Ordered Binary Decision Diagrams

### 2015-09-10 paper.tex
Add notice that OBDD and ROBDD are used synonymously
Add figure reference and fix wording

However, Bryant~\cite{BRYANT86} introduced some restrictions concerning the
ordering of the so-called \textit{decision variables} represented by the nodes
of the BDD. Furthermore, Bryant\cite{BRYANT86} was able to derive a reduced
representation of BDDs providing the DAG in a canonical form: the
\textit{Reduced Ordered Binary Decision Diagram} (\textit{ROBDD}; mostly referred
to as \textit{OBDD}, even by Bryant himself). The following section covers the
details of the OBDD representation. \tbr

>>>>

However, Bryant~\cite{BRYANT86} introduced some restrictions concerning the
ordering of the so-called \textit{decision variables} represented by the nodes
of the BDD. Furthermore, Bryant\cite{BRYANT86} was able to derive a reduced
representation of BDDs providing the DAG in a canonical form: the
\textit{Reduced Ordered Binary Decision Diagram} (\textit{ROBDD}; mostly referred
to as \textit{OBDD}, even by Bryant himself). In this paper, the terms ROBDD and
OBDD are used synonymously.

Figure~\ref{fig:obdd} shows one possible ROBDD representation of
$f=(A \land B) \lor (B \land C)$. The following section covers the details of how
to derive the OBDD representation from a BDD. \tbr
